### 2018-08-08 paper/related.tex

Cloud services for availability of files on multiple devices and sharing with others, such as Dropbox, Box, or iCloud, require trust in the service provider, at minimum to keep the service running without changes to the terms of service that would make them unacceptable. Alternatively, users could set up their own cloud using a dedicated server or edge device such as a home gateway. This would require equipment that users are less likely to already have than laptops or smartphones.

There have been several fully implemented attempts at P2P storage, mostly for backup, such as Wuala\footnote{http://www.wuala.com} (later changed to client-server architecture, now closed down), Farsite~\cite{farsite} (no longer in use), Nebulostore~\cite{nebulo} (maintained but not deployed). They deliberately use storage and replication on other peers, something we aim to avoid, even though the privacy risk is reduced compared to a central provider.

P2P file sharing has been researched extensively, with respect to aspects such as architecture (starting with the semi-centralized Napster, then decentralized Gnutella), availability and replication~\cite{replica}, scalability (Bittorrent~\cite{bittorrent-incentives}), anonymity (Freenet~\cite{Clarke:2001}, Tor~\cite{Tor}), and distributed hash tables (DHT) such as CAN, Chord, Pastry, and Tapestry (see \cite{dhtchurn} for an overview). In contrast to our work, the main goal was to enable dissemination to many users who do not necessarily know each other in person. Here, we focus on sharing files in a more deliberate yet ad-hoc manner, \ie between users that out-of-band agree to share a file but do not keep it available for anyone else in the future.

@@

Onion routing schemes, with infrastructure and governance (Tor~\cite{Tor}) and without (I2P~\footnote{https://geti2p.net/en/}), though geared toward web browsing, come closest to file transfer without third-party storage. They do not, however, allow for unreliable user devices as relay nodes.

The main concern, shared with traditional P2P file sharing, is churn~\cite{dhtchurn} and its effect on availability. % - here in the narrow context of the set of user devices based on user behavior. 
The commonly used approach of replication and redundancy used to handling churn does not work in our case as we prioritize privacy and independence from third-party storage.

>>>>

Cloud services that replicate files across multiple devices and help share them with other users (e.g. \emph{Dropbox}, \emph{Box}, or \emph{iCloud}) require trust in the service provider, at a minimum to keep the service running without changes to the terms of service that would make them unacceptable. Alternatively, some solutions (such as the \emph{NextCloud} stack, or the \emph{FreedomBox} distribution) allows users to set up their own domestic cloud using a dedicated server or edge device such as a home gateway. These approaches however require equipment that users are less likely to possess already compared to laptops or smartphones.

There have been several fully implemented attempts at P2P storage, mostly for backup, such as \emph{Wuala}\footnote{http://www.wuala.com} (later changed to a client-server architecture, now closed down), \emph{Farsite}~\cite{farsite} (no longer in use), \emph{Nebulostore}~\cite{nebulo} (maintained but not deployed). They deliberately use storage and replication on other peers. Even though the privacy risks of these solutions is reduced compared to central providers, we avoid any form of replication in \ac{SPORES} voluntarily, both to limit unneeded storage overheads, and to increase privacy guarantees.

P2P file sharing has been researched extensively, with respect to aspects such as architecture (starting with the semi-centralized Napster, then decentralized Gnutella), availability and replication~\cite{replica}, scalability (Bittorrent~\cite{bittorrent-incentives}), anonymity (Freenet~\cite{Clarke:2001}, Tor~\cite{Tor}), and distributed hash tables (DHT) such as CAN, Chord, Pastry, and Tapestry (see \cite{dhtchurn} for an overview). In contrast to our work, these efforts principally aimed at enabling dissemination to many users who do not necessarily know each other in person. With \ac{SPORES}, we focus on sharing files in a more deliberate yet ad-hoc manner, \ie between pairs of users that out-of-band agree to share a file but do not keep it available for anyone else in the future.

@@

Onion routing schemes, with infrastructure and governance (Tor~\cite{Tor}) and without (I2P\footnote{https://geti2p.net/en/}), though geared toward web browsing, come closest to file transfer without third-party storage. They do not, however, allow for unreliable user devices as relay nodes, as we do.

The main concern arising from unreliable nodes, which is shared with traditional P2P file sharing, is \emph{churn}~\cite{dhtchurn} and its effect on availability. % - here in the narrow context of the set of user devices based on user behavior. 
Most P2P approaches have addressed churn in the past by combining in various ways \emph{data replication} (e.g. by storing the same file chunk on multiple nodes) and \emph{routing redundancy} (e.g. by maintaining multiple independent paths to the same node). Data replication does not work in our case as we prioritize privacy and independence from third-party storage. The probabilistic onion routing we propose can be interpreted as a form of routing redundancy, albeit one that is built from the ground up to ensure strong privacy guaranties.

% The commonly used approach of replication and redundancy used to handling churn does not work in our case as we prioritize privacy and independence from third-party storage.

### 2018-08-08 paper/spor.tex

\commentAL{When is CreateHeader used?}

There are many uses of Sphinxes, many criteria that can be used to select the 
nodes in each layer.
We will focus on maximizing availability when routing in a network with high 
churn, but one could equally well select nodes to maximize, \eg, bandwidth.
We now describe a protocol, \ac{SPOR}, which uses Sphinxes to transfer messages 
from a source to a destination over a network of nodes with high churn.

>>>>

There are many uses of \Sphinxes, many criteria that can be used to select the 
nodes in each layer.
We will focus on maximizing availability when routing in a network with high 
churn, but one could equally well select nodes to maximize, \eg, bandwidth.
We now describe a protocol, \ac{SPOR}, which uses \Sphinxes to transfer messages 
from a source to a destination over a network of nodes with high churn.
